\section{Collection of TO DOs removed from the paper on 16. Oktober}

\paragraph{Stuff to ask HW}
\begin{itemize}
\item The Binney 2012b reference on "use axisymmetric potential + DF" for recovering the potential is not quite the thing - he is more focused on DF in this paper. Is there another reference I should use?
\end{itemize}

\paragraph{Stuff to be worked out by Wilma}
\begin{itemize}
\item Introduction mentions Binney 2011 reference in first sentence. Check, what this reference says, and if we can reference it here.
\item Check again, that all references are used.
\item For all Binney \& Tremaine 2008 references include the corresponding section.
\item Absätze mit Indent. Keine Leerzeilen.
\item Do not use r as distance from sum. Maybe use $D$ or $d$????
\item Satz ueber flattened Staeckel potentials brauch noch ne Referenz (Email an Glenn geschrieben --> He answered... Include it in second version for referee).
\item Thank sanders.
\item How did I loose the McMillan 2011 reference: %\bibitem[McMillan(2011)]{2011MNRAS.414.2446M} McMillan, P.~J.\ 2011, \mnras, 414, 2446 %[TO DO] mcm11
\end{itemize}

\paragraph{Stuff I might ignore}
\begin{itemize}
\item Overall, Table 3 could do with a little less information.
\item Look up what McMillan \& Binney 2013 have to say about the numerical accuracy of the normalisation. Sanders \& Binney (2015) are quoting them on that matter.
\item Potential tests, Figures 18-20: Redo whole analysis with vcirc not being fixed (HW is not sure if this really doesn't make a difference.]
\item Error plots: some of the 25 MC sample analyses have to be re-done.
\item Abstract seems too long.
\item emulateapj doesn't know NAR in the http://adsabs.harvard.edu/abs/2013NewAR..57...29B reference
\end{itemize}


%=====================================================

\section{Bigger questions that I will ignore}

\paragraph{Questions that haven't been covered so far:}
\begin{itemize}
\item What happens, when the errors are not uniform?
\item What if errors in distance matter for selection?
\end{itemize}

\paragraph{Stuff that needs to be further examined in fig. \ref{fig:wedFlexVol_bias_vs_SE} about the survey volume:}
\begin{itemize}
\item[[TO DO]] Maybe add volume at smaller radius with large vertical extent?
\item[[TO DO]] Do we explicitely want to test, if it matters, if the radial coverage is larger or smaller the disk scale length, and the vertical coverage is larger or smaller than the disk scale height?
\end{itemize}

\paragraph{Stuff that needs to be further examined about the robustness against data incompleteness:}
\begin{itemize}
\item[[TO DO]] Make similar test as isoSphFlexIncompR, but with KKS potential, to test, if this robustness is a special case for the isochrone potential.
\end{itemize}

%=====================================================

%15. May 2015 --> Meet with HW to write
%
%* Priors: We want parameter estimates that alre tight enough, such that it does not matter, if we had assumed a flat or a logarithmically flat prior



