\section{Results} \label{sec:results}

We are now in a position to explore the questions about the ultimate limitations of action based modelling, posed in the introduction: 
\begin{itemize}
\item Can we still retrieve unbiased  model parameter estimates $p_M$ in the limit of large sample sizes? 
\item What role does the survey volume and geometry play, at given sample size? 
\item What if our knowledge of the sample selection function is imperfect, and potentially biased? 
\item How do the parameter estimates deteriorate if the individual errors on the phase-space coordinates become significant? 
\end{itemize}
But we also consider the more fundamental limitations:
\begin{itemize}
\item What if the observed stars are not extacly drawn from the family of model distribution functions? 
\item What happens to the estimate of the potential and the DF, if the actual potential is not contained in the family of model potentials?
\end{itemize}
We do not explore the breakdown of the assumption that the system is axisymmetric and in steady state. Except of the test suite on measurement errors in \S\ref{sec:results_errors}, we assume that the phase-space errors are negligible.


%=========================================


\begin{deluxetable}{lllll}%{p{0.1\textwidth}p{0.1\textwidth}p{0.25\textwidth}p{0.25\textwidth}p{0.05\textwidth}}
\tabletypesize{\scriptsize}
%\rotate
\tablecaption{Summary of test suites in this work: The first column indicates the test suite, the second column the potential, DF and selection function model etc. used for the mock data creation, the third model the corresponding model assumed in the analysis, and the last column lists the figures belonging to the test suite. Parameters that are not left free in the analyis, are always fixed to their true value. Unless otherwise stated we calculate the likelihood by the nested-grid and MCMC approach outlined in \S\ref{sec:fitting} and use $N_\text{spatial} = 16$, $N_\text{velocity} = 24$, $N_\text{sigma} = 5$ as numerical accuracy for the likelihood normalisation in Eq. ???. [TO DO: Change encircled numbers to proper order. Make sure the plot references are the right ones.] \label{tbl:tests}}
\tablewidth{0pt}
\tablehead{
\colhead{Test} & & \colhead{Model for Mock Data}  & \colhead{Model in Analysis} & \colhead{Figures}}
\startdata
\textcircled{1}         & \emph{Potential:}     & "KKS-Pot" & - & Mock data: \\
Influence of            & \emph{\MAP:}          & 2 \MAPs "hot" or "cold" qDF   &   & Fig. \ref{fig:mockdatadistr}\\
survey volume on        & \emph{Survey volume:} & a) $R \in [4,12]$ kpc,$z \in [-4,4]$ kpc, $\phi \in [-20^\circ,20^\circ]$. &  & \\
mock data distribution, &                       & b) $R \in [6,10]$ kpc,$z \in [1,5]$ kpc, $\phi \in [-20^\circ,20^\circ]$.&  & \\
also in action space	& \emph{\# stars per data set:} & 20,000 &  & \\
						& \emph{\# data sets:}   & 4 (= $2\times 2$ models) & & \\

\tableline
\textcircled{9}         & \emph{Potential:}     & "Iso-Pot", "MW13-Pot" \& "KKS-Pot" & - & Convergence\\
Numerical accuracy      & \emph{\MAP:}          & "hot" qDF                          &   & of normalisation:\\
in calculation          & \emph{Survey volume:} & sphere around sun, $r_\text{max} = 0.2, 1, 2, 3$ or $4$ kpc &   & Fig. \ref{fig:norm_accuracy}\\
of the likelihood       & \emph{Numerical accuracy:} & $N_\text{spatial}\in[5,20]$, $N_\text{velocity}\in[6,40]$, $N_\text{sigma}\in[3.5,7]$& & \\
normalisation           &                       & & & \\
										   
\tableline
\textcircled{10}        & \emph{Potential:}     & "Iso-Pot" & "Iso-Pot", all parameters free & Fig. \ref{fig:triangleplot}\\
\pdf is a               & \emph{\MAP:}          & "hot" qdf & qDF, all parameters free & \\
multivariate            & \emph{Survey Volume:} & sphere around sun, $r_\text{max} = 2$ kpc & (fixed \& known) & \\
Gaussian                & \emph{\# stars per data set:} & 20,000 & & \\
for large data sets.	& \emph{\# data sets:}   & 5 (only one is shown) & & \\
                        & \emph{Numerical accuracy:} & & $N_\text{velocity} = 20$ and $N_\text{sigma} = 4$ & \\

\tableline
\textcircled{2}			& \emph{Potential:}     & "Iso-Pot" & "Iso-Pot", free parameter: $b$ & Fig. \ref{fig:sqrtN}\\
Width of the			& \emph{\MAP:}          & "hot" qDF & "hot" qDF, free parameters: & \\
likelihood scales       &                       &           & $\ln\left(\frac{h_R}{8\text{kpc}}\right),\ln\left(\frac{\sigma_{R}}{230 \text{km s}^{-1}}\right),\ln\left(\frac{h_{\sigma,R}}{8\text{kpc}}\right)$ & \\
with number of stars    & \emph{Survey volume:} & sphere around sun, $r_\text{max} = 3$ kpc   & (fixed \& known) & \\
by $\propto 1/\sqrt{N}$.& \emph{\# stars per data set:} & between 100 and 40,000 &  & \\ 
                        & \emph{\# data sets:}  & 132 & & \\                                       
                        & \emph{Analysis method:} & & likelihood on grid & \\
                        & \emph{Numerical accuracy:} & & $N_\text{velocity} = 20$ and $N_\text{sigma} = 4$ (for speed) & \\

\tableline
\textcircled{3}         & \emph{Potential:}     & 2 "Iso-Pot" with & "Iso-Pot", free parameter: $b$ & Fig. \ref{fig:centrallimittheorem}\\
Parameter estimates     &                       & $b=0.8$ kpc or $b=1.5$ kpc & \\
are unbiased.           & \emph{\MAP:}          & 2 \MAPs, "hot" or "cool" qDF  & "hot"/"cool" qDF, free parameters: & \\
                        &                       &                          & $\ln\left(\frac{h_R}{8\text{kpc}}\right),\ln\left(\frac{\sigma_{R}}{230 \text{km s}^{-1}}\right),\ln\left(\frac{h_{\sigma,R}}{8\text{kpc}}\right)$ & \\
                        & \emph{Survey volume:} & 5 spheres around sun, $r_\text{max} = 0.2, 1, 2, 3$ or $4$ kpc & (fixed \& known) & \\
                        & \emph{\# stars per data set:} & 20,000 & & \\
                        & \emph{\# data sets:}  & 640 (= $2\times2\times5$ models $\times 32$ realisations) & & \\
                        & \emph{Analysis method:} & & likelihood on grid & \\
                        & \emph{Numerical accuracy:} & & $N_\text{velocity} = 20$ and $N_\text{sigma} = 4$ (for speed) & \\

\tableline
\textcircled{4} 		& \emph{Potential:} 	& i) "Iso-Pot", ii) "MW13-Pot" or iii) "KKS-Pot" 	& i) "Iso-Pot", all parameters free & Fig. \ref{fig:wedFlexVol_bias_vs_SE} \\
Influence of 			& 						& 													& ii) "MW13-Pot", $R_d$ and $f_h$ free & \\
position \& shape 		& 						& 													& iii) "KKS-Pot", all free except $v_\text{circ}(R_\odot)$ & \\
of survey volume 		& \emph{\MAP:}			& "hot" qDF 										& i) \& iii) qDF, all parameters free & \\
on parameter recovery 	& 						& 													& ii) qDF, only $h_R$, $\sigma_{z,0}$ and $h_{\sigma_R}$ free& \\
						& \emph{Survey volume:}	& 4 different wedges, see Fig. \ref{fig:wedFlexVol_bias_vs_SE}, upper right panel & (fixed \& known) & \\
						& \emph{\# of stars per data set:} & 20,000 & & \\
						& \emph{\# data sets:}	& 48 (= $4\times3$ models $\times 4$ realisations) & & \\
						& \emph{Analysis method:} & & i) \& ii) MCMC, iii) likelihood on grid & \\
						& \emph{Action calculation:} & ii) \& iii) low accuracy & (same as mock data creation) & \\
						&						& "St\"{a}ckel Fudge" grid \citep{bov15} for speed && \\
						&						& (\# grid points: 25 in each $E$ and $\psi$, && \\
						&						& 30 in $L_z$, $R_\text{max}=5$  & & \\
						&						& [TO DO: What is psi and Rmax (units)?]) & & \\
\tableline
\textcircled{5}         & \emph{Potential:}     & "Iso-Pot" & "Iso-Pot", all parameters free & Illustration \& mock data: \\
Influence of            & \emph{\MAP:}          & 2 \MAPs, a) "hot" or b) "cool" qDF & qDF, all parameters free &  Fig. \ref{fig:incompR_mockdata} \& \ref{fig:incompZ_mockdata} \\
wrong assumptions       & \emph{Survey volume:} & sphere around sun, $r_\text{max} = 3$ kpc & (fixed \& known) & Analysis results: \\
about the data set      & \emph{Completeness:}  & \emph{Example 1:} radial incompleteness,  & data set complete, & Fig. \ref{fig:isoSphFlexIncompR_violins} \& ??? \\
(in-)completeness       &                       & completeness$(r) = 1-\epsilon_r \frac{r}{r_\text{max}}$, twenty $\epsilon_r \in [0,0.7]$ & completeness$(r)$ = 1, $\epsilon_r=0$& Analysis results\\
on parameter recovery   &                       & $r \equiv$ distance from sun, & & when not using $v_T$ data: \\
                        &                       & \emph{Example 2:} planar incompleteness,  & data set complete, & Fig. \ref{fig:isoSphFlexIncomp_marginal_violins}\\
                        &                       & completeness$(z) = 1-\epsilon_z \frac{|z|}{r_\text{max}}$, $\epsilon_r \in [0,0.7]$, & completeness$(r)$ = 1, twenty $\epsilon_z=0$& \\
                        &                       & $z \equiv$ distance from Gal. plane. & & \\
                        & \emph{\# stars per data set:} & 20,000 & & \\
                        & \emph{\# data sets:}  & 40 (= $2 \times 2 \times 20$) & & \\
\tableline
\textcircled{6} & [TO DO] & & & \\
Measurement errors & & & & \\
\tableline
\textcircled{7}         & \emph{Potential:} & "Iso-Pot" & "Iso-Pot", all parameters free & mock data:\\
Deviations in the       & \emph{\MAP:}      & mix of two qDFs & single qDF, all parameters free & Fig. \ref{fig:isoSphFlexMix_mockdata_residuals}\\
assumed DF              &                   & \emph{Example 1:} with fixed qDF parameters,  & & Analysis results:\\
from the                &                   & but 20 different mixing rates: & & \ref{fig:isoSphFlexMixCont} \& Fig. \ref{fig:isoSphFlexMixDiff}\\
star's true DF          &                   & a) "hot" \& "cooler" qDF or b) "cool" \& "hotter" qDF & & \\
                        &                   & \emph{Example 2:} 20 fixed 50/50 mixtures,  & & \\
                        &                   & with varying qDF parameters (by $X\%$): & & \\
                        &                   & a) "hot" \& "colder" qDF or b) "cool" \& "warmer" qDF & & \\
                        & \emph{Survey volume:}& sphere around sun, $r_\text{max}=2$ kpc & (fixed \& known) & \\
                        & \emph{\# stars per data set:} & 20,000 & & \\
                        & \emph{\# data sets:}  & 40 (= $2 \times 2 \times 20$) & & \\
                        \tableline
\textcircled{8}			&  \emph{Potential:} & "MW14-Pot" & "KKS-Pot", all parameters free, & potential contours: \\
Deviations of the		&                    &            & only $v_\text{circ}(R_\odot)=230 \text{km s}^{-1}$ fixed & Fig. \ref{fig:MW14vsKKS2SphFlex} \\
assumed potential model	& \emph{\MAP:}       & "hot" or "cool" qDF & qDF, all parameters free & qDF recovery: \\
from the star's			& \emph{Survey volume:} & sphere around sun, $r_\text{max} = 4$ kpc & (fixed \& known) & Fig. \ref{fig:MW14vsKKS2SphFlex_violins}\\
true potential			& \emph{\# stars per data set:} & 20,000 & & \\
						& \emph{\# data sets:} & 2 & & \\
\enddata
\end{deluxetable}
