\begin{abstract}
We present \RM, a dynamical modelling machinery that aims to recover the Milky Way's (MW) gravitational potential and the orbit distribution of stellar mono-abundance populations (\MAP) in the Galactic disk \citep{bov13,bin11,bin12}. \RM is a full likelihood analysis that models the observed positions and velocities of \MAP stars with an equilibrium, three-integral quasi-isothermal distribution function (qDF) in an axisymmetric potential. In preparation for the application to the large data sets of modern Galactic surveys like Gaia, we create and analyze a large suite of mock data sets and develop qualitative "rules of thumb" which characteristics and limitations of data, model and machinery affect constraints on the potential and qDF most. We find that, while the precision of the recovery increases with the number of stars, the numerical accuracy of the likelihood normalisation becomes increasingly important and dominates the computational efforts. The modelling has to account for the survey's selection function, but \RM seems to be very robust against small misjudgments of  the data completeness. Large radial and vertical coverage of the survey volume gives in general the tightest constraints. But no observation volume of special shape or position and stellar population should be clearly preferred, as there seems to be no stars that are on manifestly more diagnostic orbits. [TO DO: Write about results on measurement errors] We investigate how small deviations of the stars' distribution from the assumed qDF affect the modelling: Having less stars at small Galactocentric radii $R$ and with lower velocities as predicted by the qDF recovers the potential more reliably than having too many stars at small $R$ and with higher velocities. The deviations of the true orbit distribution from the qDF introduced by binning stars into \MAPs in the ([Fe/H],[$\alpha$/Fe]) plane and due to abundance errors do not matter much, as long as the qDF parameters of two neighbouring \MAPs do not vary more than 20\% [TO DO: CKECK]. As the modelling has to assume a parametric form for the gravitational potential, deviations from the true potential have to be expected. We find, that in the axisymmetric case we can still hope to find a potential that is indeed a reliable best fit within the limitations of the assumed potential. Overall \RM works as a reliable and unbiased estimator, and is robust against small deviations between model and the "real world". 
\end{abstract}





