\section{Summary and Discussion} \label{sec:discussionsummary}

\Wilma{[TO DO: Introduce DF somewhere - use DF wherever we don't need qDF.] [TO DO: Introduce MW somewhere.]}
\\\Wilma{[TO DO: Compare these sections with the results. Points should be made detailed in the results section and short here in the discussion. Says Hans-Walter.]}
\\\Wilma{[TO DO: Absätze mit Indent. Keine Leerzeilen.]}

%Setting the Context
Recently, implementations of action DF-based modelling of 6D data in the Galactic disk have been put forth, in part to lay the ground-work fo Gaia (BR13; \citealt{,2013MNRAS.433.1411M,2014MNRAS.445.3133P,2015MNRAS.449.3479S}).

%Everything in a nutshell
We present \RM{}, an improved implementation of the dynamical modelling machinery of BR13, to recover the MW's gravitational potential by fitting an orbit distribution function to stellar populations within the Galactic disk. In this work we investigated the capabilities, strengths and weaknesses of \RM{} by testing its robustness against the breakdown of some of its assumptions---for well-defined, isolated test cases using mock data. Overall the method works very well and is reliable, even when there are small deviations of the model assumptions from the real world Galaxy.

%The RM code
\RM{} applies a full likelihood analysis and is statistically well-behaved. It goes beyond BR13 by allowing for a straightforward and flexible implementation of different model families for potential and DF. It also accounts for selection effects by using full 3D selection functions (given some symmetries).\\

\noindent {\bf Computational speed:~} Large data sets in the age of Gaia require increasingly accurate likelihood evaluations and flexible models. To be able to deal with these computational demands, we sped up the \RM{} code by combining a nested grid approach with MCMC and by faster action calculation using the St\"{a}ckel \citep{2012MNRAS.426.1324B} interpolation grid by \citet{2015ApJS..216...29B}. However, application of \RM{} to millions of stars will still be a task for supercomputers and calls for even more improvements and speed-up in the fitting machinery.\\

\noindent {\bf Properties of the data set:~} We could show that \RM{} can provide potential and DF parameter estimates that are very accurate (i.e. unbiased) and precise in the the limit of large datasets, as long as the modelling assumptions are fulfilled.
\\We also found that the \emph{location} of the survey volume within the Galaxy matters little. At given sample size a larger survey \emph{volume} with large coverage in \emph{both radial and vertical} direction will give the tightest constraints on the model parameters.
\\Stellar populations of different scale length and temperature probe different regions of the Galaxy (BR13). But there is no easy rule of thumb for which survey volume and stellar population which potential and DF parameter is constrained best.\HW{[TO DO: Ask HW, if he wants this to be discussed somewhere in detail.]}
\\Surprisingly, (cf. \citealt{2013A&ARv..21...61R}) \RM{} seems to be very robust against misjudgements of the spatial data selection function. We speculate that this is because missing stars in the data set do not affect the measured rotation curve, which contains information about the potential.
\\\Wilma{[TO DO: Fiished up to here. Continue here.]} \Wilma{[TO DO: Comment from HW: Author: rix Subject: This paragraph shouldbe 1 or 2 sentences, following the first paragraph on "Sample/Data Properties". This -- at the moments --reads to bequite confusing. I don't quite get whatthe "upshot" is; there is technical detai on $N_{error}$ [enought to say it's expensive]; and, as noted earlier; I don't understand why theerror convolution for a nearbydata point needs to know about $\delta v_\text{max}$]} Properly convolving the likelihood with measurement errors is computational very expensive. By ignoring positional errors and only including distance errors as part of the velocity error, we can drastically reduce the computational costs. For stars within 3 kpc from the Sun this approximation works well for distance errors of $\sim 10\%$ or smaller. The number of MC samples needed for the error convolution using MC integration scales by $N_\text{error} \propto (\delta v_\text{max})^2$ with the maximum velocity error at the edge of the sample. If we did not know the true size of the proper motion measurement errors perfectly, we can only reproduce the true model parameters to within $\lesssim 2$ sigma \Wilma{[TO DO: Check???]} as long as we do not underestimate it by more than $10\%$ and for proper motion errors $\lesssim 2 \text{ mas yr}^{-1}$.\\

%\subsection{Data Deviations from the Modelling Assumptions about the Distribution Function and the Potential}

\noindent {\bf Deviations from the qDF Assumption:~} \RM{} assumes that stellar sub-populations can be described by simple DFs. We investigated how much the modelling would be affected if the assumed family of DFs would differ from the star's true DF.
\\In Example 1 in Section \ref{sec:results_mixedDFs} we considered a) a hot DF with less stars at small radii and more stars with low velocities than assumed (reddish data sets in Figure \ref{fig:isoSphFlexMix_mockdata_residuals}), and b) a cool DF with broader velocity dispersion wings and less stars at large radii than assumed (bluish data sets). \HW{[TO DO: I removed the radius mock data distribution from the figure, because you couldn't see differences. Should I put it back in, so people understand this comment better?]} We find that case a) would give more reliable results for the potential parameter recovery, but in both cases biases are small if the contamination is less than [TO DO: CHECK] \Jo{[TO DO: Jo suggested this last part of the sentence, but I'm not sure, this is the case]}. In other words, hotter stellar populations appear to be more robust against pollution of stars coming from a cooler population than vice versa. 
\\Binning of stars into \MAPs{} in $[\alpha/\mathrm{Fe}]$ and $[\mathrm{Fe}/\mathrm{H}]$, as done by BR13, could introduce biases due to abundance errors or too large bin sizes---always assuming \MAPs{} follow simple DF families (e.g., the qDF). In Example 2 in Section \ref{sec:results_mixedDFs} we found that, in the case of 20,000 stars per bin, differences of $20\%$ in the qDF parameters of two neighbouring bins can still give quite good constraints on the potential parameters.
\\The relative difference in the qDF parameters $\sigma_{R,0}$ and $\sigma_{z,0}$ of neighbouring \MAPs{} in Figure 6 of BR13 (which have bin sizes of $[\mathrm{Fe}/\mathrm{H}] = 0.1$ dex and $\Delta [\alpha/\mathrm{Fe}] = 0.05$ dex) are indeed smaller than $20\%$. Figure \ref{fig:isoSphFlexMixCont} and \ref{fig:isoSphFlexMixDiff} suggest that especially the tracer scale length $h_R$ needs to be recovered to get the potential right. For this parameter however the bin sizes in Figure 6 of BR13 might not yet be small enough to ensure no more than $20\%$ of difference in neighbouring $h_R$.


\Wilma{[TO DO: Include the following comments by Jo somewhere: This is a general approach of fitting action-based disk DFs for getting the potential. The qDF is a specific example that we use in this paper. In futures studies different forms of DFs might be fitted to data.  That the results are quite robust to the form of the DF not entirely correct motivates this further.]}

\noindent {\bf Gravitational Potential beyond the Parameterized Functions Considered:~} \Wilma{[TO DO: Comment from HW: In style and contentthis seems verysimilar tothe RESULTSsection. We should eitherdrastically shorten the text in the results section (probably not), or here.]} In the long run \RM{} should incorporate a family of gravitational potential models that can reproduce the essential features of the MW's true mass distribution. While our fundamental assumption of the Galaxy's axisymmetry is at odds with the obvious existence of non-axisymmetries in the MW, we will not dive into investigating this implications in this paper. Instead we test how a misjudgment of the parametric potential form affects the recovery by fitting a potential of St\"{a}ckel form \citep{1994AA...287...43B} to mock data from a different potential family with halo, bulge and exponential disk. The recovery is quite successful and we get the best fit within the limits of the model. However, even a strongly flattened St\"{a}ckel potential component has difficulties to recover the very flattened mass distribution of an exponential disk. This leads to misjudgment of the qDF parameters describing the vertical action distribution, $\sigma_{z,0}$ and $h_{\sigma,z}$. As the qDF parameter $\sigma_{z,0}$ corresponds to the physical vertical velocity dispersion at the Sun, a comparison with direct measurements could be a valuable cross-checking reference. \Wilma{[TO DO: This might not be true. For isochrone and Staeckel potential I get this behaviour, but not for the MW14-Pot!!! Might be, because it's not separable??? Check!!!] [TO DO: best to simply remove it...]} In case of as many as 20,000 stars we should therefore already be able to distinguish between different potential models.
\\The advantage of using a St\"{a}ckel potential with \RM{} is firstly the exact and fast action calculation via the numerical evaluation of a single integral, and secondly that the potential has a simple analytic form, which greatly speeds up calculations of forces and frequencies (as compared to potentials in which only the density has an easy description like the exponential disk). A superposition of several simple Kuzmin-Kutuzov St\"{a}ckel components can successfully produce MW-like rotation curves (see \citet{1994AA...287...43B}, \citet{2003MNRAS.340..752F} and Figure \ref{fig:MW14vsKKS2SphFlex}) and one could think of adding even more components for more flexibility, for example a small roundish component for the bulge. \Wilma{[TO DO: Comment by Jo: In a sense the two approaches (a) using the Staeckel action approximation with a MW like potential and (b) using a Staeckel potential directly are dong the same thing (approximating the true potential as a Staeckel potential). The question is which is best.]}
\\The potential model used by BR13 had only two free parameters (disk scale lentgh and halo contribution to $v_\text{circ}(R_\odot)$. To circumvent the obvious disadvantage of this being at all not flexible enough, they fitted the potential separately for each \MAP{} and recovered the mass distribution for each \MAP{} only at that radius for which it was best constrained - assuming that \MAPs{} of different scale length would probe different regions of the Galaxy best. Based on our results in Figure \ref{fig:MW14vsKKS2SphFlex} this seems to be indeed a sensible approach \Jo{[TO DO: Check that this is indeed the case - it is not clear to me from the plot. ???]}.
\\We suggest that combining the flexibility and computational advantages of a superposition of several St\"{a}ckel potential components with probing the potential in different regions with different \MAPs{} as done by BR13, could be a promising approach to get the best possible constraints on the MW's potential.\\

%\subsection{Different Modelling Approaches using Action-based Distribution Functions}

{\bf Different Modelling Approaches using Action-based Distribution Functions:~} We have focussed for the time being on \MAPs{} for a number of reasons: First, they seem to permit simple DFs \citep{bov12b,bov12c,2012ApJ...753..148B}, i.e., approximately qDFs \citep{2013MNRAS.434..652T}. Second, all stars, e.g., those from different \MAPs{}, must orbit in the same potential. Therefore each \MAP{} will and can yield quite different DF parameters; but each \MAP{} will also provide a (statistically) independent estimate of the potential parameters. At the same time---if all is well---those potential parameters, derived from different \MAPs{}, should be mutually consistent. In some sense, this approach focusses on constraining the potential, treating the DF parameters as nuisance parameters.
\\The main drawback is that we have many astrophysical reasons that the DF properties (for reasons of galaxy evolution and chemical evolution) are astrophysically linked between different \MAPs{}. Ultimately, the goal is to do a fully consistent chemodynamical model that simultaneously fits the potential and $\text{DF}(\vect{J},\text{[X/H]})$ simultaneously (where [X/Fe] denotes the full abundance space) with a full likelihood analysis. This has not yet been attempted here, because the behaviour is quite complex. 
\\Since the first application of \RM{} by BR13 there have been two similar efforts to constrain the Galactic potential and/or orbit distribution using action-based distribution functions:
\\\citet{2014MNRAS.445.3133P} fitted both potential and a $f(\vect{J})$ to giant stars from the RAVE survey \citep{2006AJ....132.1645S} and the vertical stellar number density profiles in the disk by \citet{2008ApJ...673..864J}. They did not include any chemical abundances in the modelling. Instead, they used a superposition of action-based DFs to describe the overall stellar distribution at once: a superposition of qDFs for cohorts in the thin disk, a single qDF \Wilma{[TO DO: CHECK]} for the thick disk stars and an additional DF for the halo stars. Taking proper care of the selection function requires a full likelihood analysis and the calculation of the likelihood normalisation is computational expensive. \citet{2014MNRAS.445.3133P} choose to circumvent this problem by directly fitting a) histograms of the three velocity components in eight spatial bins to the velocity distribution predicted by the DF and b) the vertical density profile predicted by the DF to the profiles by \citet{2008ApJ...673..864J}. The vertical force profile of their best fit mass model nicely agrees with the results from BR13 for $R>6.6$ kpc. The disadvantage of their approach is, that by binning the stars spatially, a lot of information is not used.
\\\citet{2015MNRAS.449.3479S} have focussed on understanding the abundance-dependence of the DF, relying on a fiducial potential. They developed extended distribution functions, i.e., functions of both actions and metallicity for a superposition of thin and thisk disk, each consisting of several cohorts described by qDFs, a DF for the halo, a functional form of the metallicity of the interstellar medium at the time of birth, and a simple prescription for radial migration. They applied a full likelihood analysis accounting for selection effects and found a best fit for the eDF in a fixed fiducial potential by \citet{1998MNRAS.294..429D} to the stellar phase-space and metallicity \Wilma{[TO DO: CHECK]} data of the Geneva-Copenhagen Survey \citep{2004A&A...418..989N,2009A&A...501..941H} and the stellar density curves by \citet{1983MNRAS.202.1025G}. Their best fit predicted the velocity distribution of SEGUE G dwarfs quite well, but had biases in the metallicity distribution, which they accounted to being a problem with the SEGUE metallcities. \\

%\subsection{On the Assumption of Axisymmetry}

We know that real galaxies, including the Milky Way, are not axisymmetric. Using N-body models, we will explore in a subsequent paper what when data from a non-axisymmetric system get interpreted through axisymmetric modelling.

\HW{[TO DO: Comment from Jo: Maybe we also want a conclusion with a simple bullet-point list of the main conclusions discussed in detail in the Discussion section.]}
