We are now in a position to explore the questions about the ultimate limitations of action based modelling, posed in the introduction: 
\begin{itemize}
\item Can we still retrieve unbiased  model parameter estimates $p_M$ in the limit of large sample sizes? 
\item What role does the survey volume and geometry play, at given sample size? 
\item What if our knowledge of the sample selection function is imperfect, and potentially biased? 
\item How do the parameter estimates deteriorate if the individual errors on the phase-space coordinates become significant? 
\end{itemize}
But we also consider the more fundamental limitations:
\begin{itemize}
\item What if the observed stars are not extacly drawn from the family of model distribution functions? 
\item What happens to the estimate of the potential and the DF, if the actual potential is not contained in the family of model potentials?
\end{itemize}
We do not explore the breakdown of the assumption that the system is axisymmetric and in steady state.
[{\bf hat shouldl also be at the end of the introduction..}
[say: except for the case of ``errors'' we assume that thne phase-space errors are negligible..]


%=========================================


\begin{deluxetable}{lllll}%{p{0.1\textwidth}p{0.1\textwidth}p{0.25\textwidth}p{0.25\textwidth}p{0.05\textwidth}}
\tabletypesize{\scriptsize}
%\rotate
\tablecaption{[TO DO: Caption]\label{tbl:tests}}
\tablewidth{0pt}
\tablehead{
\colhead{Test} & & \colhead{Model for Mock Data}  & \colhead{Model in Analysis} & \colhead{Figures}}
\startdata
\textcircled{1}                    & \emph{Potential:}             & "KKS-Pot"                  & -  & Fig. \ref{fig:mockdatadistr}\\
Influence of                       &  \emph{\MAP:}                   & "hot" \& "cold" qDF   &   &                                                 \\
survey volume on            & \emph{Survey volume:}   & a) $R \in [4,12]$ kpc,  &  & \\
mock data distribution,  &                                             & $z \in [-4,4]$ kpc, &  & \\
also in action space	   &                                             & $\phi \in [-20^\circ,20^\circ]$. &  & \\
										   &                                             & b) $R \in [6,10]$ kpc, &  & \\
										   &                                             & $z \in [1,5]$ kpc, &  & \\
										   &                                             & $\phi \in [-20^\circ,20^\circ]$. &  & \\
										   & \emph{\# stars per data set:} & 20,000 &  & \\
										   & \emph{\# data sets:}   & 4 & & \\

										   
\tableline
\textcircled{2}				& \emph{Potential:} & "Iso-Pot" & "Iso-Pot", free parameter: $b$ & Fig. ???\\
Width of the					& \emph{\MAP:}        & "hot" qDF & "hot" qDF, free parameters: & \\
likelihood scales			&                                  &                   & $\ln\left(\frac{h_R}{8\text{kpc}}\right),\ln\left(\frac{\sigma_{R}}{230 \text{km s}^{-1}}\right),\ln\left(\frac{h_{\sigma,R}}{8\text{kpc}}\right)$ & \\
with number of stars	& \emph{Survey volume:} & sphere around sun,   & & \\
by $\propto 1/\sqrt{N}$&                                           & $r_\text{max} = 3$ kpc & & \\
										   & \emph{\# stars per data set:} & between 100 and 40,000 &  & \\
										   & \emph{\# data sets:}   & 132 & & \\
\enddata
\end{deluxetable}

[TO DO: Make consistent $h_{\sigma_R}$ --> $h_{\sigma,R}$]